Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-04-14 ms.tex
finishing matching conditions section

We employ an expansion in terms of spherical Bessel functions in $r$ and a Laplace expansion with the imaginary frequency variable $s=-i\omega$. The eigenvalues $s$ are real and negative for damped solutions to the time-dependent equation. The expansion for $J(r, \sigma, t)$ is

\be
\label{eq:jrsigmat_expansion}
J(r, \sigma, t) = \sum_{n=1}^{\infty} \int \frac{ds}{2\pi i} e^{st} j_0\left(\kappa_n r\right) J(n, \sigma, s).
\ee

The definition of the Laplace transform is

\be
J(n, \sigma, s) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{-st} J(r, \sigma, t).
\ee

@@

@@

To solve the second order Equation \ref{eq:response}, starting points at large $\pm |\sigma|$ are chosen, and the dependence in Equation \ref{eq:finite_bc} is used for the starting slope. The solution is then integrated toward the singularity at $\sigma_s$ from each side. The two starting values are varied until $J(n,\sigma,\omega)$ is continuous at $\sigma_s$ and satisfies the desired jump in slope in Equation \ref{eq:discontinuity}. Since the solution is linear in the starting conditions, only two integrations with different starting values are necessary.

>>>>

We employ an expansion in terms of spherical Bessel functions in $r$ and transform the time dependence into an imaginary frequency variable $\omega$. The eigenvalues $i\omega$ are real and positive for damped solutions to the time-dependent equation. The expansion for $J(r, \sigma, t)$ is

\be
\label{eq:jrsigmat_expansion}
J(r, \sigma, t) = -\sum_{n=1}^{\infty} \int \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega).
\ee

with

\be
J(n, \sigma, \omega) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{i\omega t} J(r, \sigma, t).
\ee

@@

\be \label{eq:diffusion_plugged_in}
 \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2J(n,\sigma,\omega)}{\partial\sigma^2} = -\frac{2\kappa_n^2}{R} \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
\ee

@@

At $\sigma=\sigma_s$ continuity must be enforced in $J$

\be \label{eq:matching_condition_1}
J_+ = J_-
\ee

and the discontinuity in $dJ/d\sigma$  must be

\be \label{matching_condition_2}
\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}
\ee

according to the differential equation. At large values of $\sigma$ the line profile is small such that Eq. \ref{eq:diffusion_plugged_in} becomes

\be \label{eq:diffusion_at_large_sigma}
\frac{\partial^2J(n, \sigma, \omega)}{\partial\sigma^2} = \frac{\Delta^2\kappa_n^2}{k^2} J.
\ee

which has solutions

\be
J(n, \sigma, \omega)\ {\sim}\ e^{\pm \Delta \kappa_n \sigma / k}
\ee

and thus

\be \label{eq:single_j_derivative}
\frac{\partial J}{\partial \sigma} = \mp \frac{\Delta\kappa_n}{k} J
\ee

where a negative sign is taken for large $+\sigma$ and a positive sign is taken for large $-\sigma$. Two numerical integrations are performed inward from large $\pm \sigma$ to the source $\sigma_s$ to isolate the solution that increases exponentially toward the line center. Initial values for integration are obtained by setting $J=1$ in Eq. \ref{eq:single_j_derivative}. This yields values for $J_\pm$ and $J'_\pm$ on either side of the source, where a prime indicates the derivative $\partial/\partial \sigma$. By enforcing the matching conditions Eqs. \ref{eq:matching_condition_1} and \ref{matching_condition_2}, the solution for $J(n, \sigma, \omega)$ is obtained everywhere in the range of photon frequencies. Since the solution is linear in the starting conditions, only two integrations with different starting values are necessary.
